### 2014-03-13 LaTeX/RhodiumEmp.tex
more mods

@@

World Bank data: Econ indicators

@@

Maybe we should begin this section by showing the distribution of econ performance among the cntry-years in the dataset. this would illustrate that there is noticeable variation in economic performance to explain.

@@

>>>>

Dependent variable: World Bank data GDP per capita growth

Key Independent variables:

@@

@@

@@

Use simulations to determine substantive effects

### 2014-03-13 LaTeX/RhodiumIntro.tex
more mods

Mexico case: high levels of violence since 2008 but little effect on economic growth

Mexico facing serious internal political stability (civil violence, civil war...) yet this has little effect on economic growth as of yet. When should we expect to see the adverse effects of civil war manifest themselves in terms of lower economic growth?

@@

>>>>

Puzzle: Why do some conflicts have immediate impacts on a country's economy while others that fester for decades have little to none.

	Mexico case: high levels of violence since 2008 but little effect on economic growth. Mexico facing serious internal political stability (civil violence, civil war...) yet this has little effect on economic growth as of yet. When should we expect to see the adverse effects of civil war manifest themselves in terms of lower economic growth?

@@

Spatial Dist Hypothesis: Location of conflicts to major cities and capitals determine effect of civil conflict on economic performance. thesis: conflicts only significantly dampens economic performance if they are a threat to major population centers. conflicts isolated in sparsely populated territories of the country have little to no effect on the whole.

### 2014-03-13 LaTeX/RhodiumLit.tex
more mods

literature on endogeneity of conflict and economic performance (sambanis 2001, worldbank 2003)

@@

literature on application of spatial variables to studying conflict and how it hasnt captures what we are doing at the sub-national level with city data

>>>>

@@

	explain how what has been done in the spatial conflict literature and even the sub-nat/spat literature does not capture what we have done in this paper

% literature on endogeneity of conflict and economic performance (sambanis 2001, worldbank 2003)

% 	do we want to wade in to the endogeneity debate? i'm not sure we do that's why i've commented this out temporarily. seems to me our life would be made easier if we just tied ourselves to teh literature that puts econ growth as the dv nad conflict as the iv. u probably know better than me if this position is untenable.

### 2014-03-13 LaTeX/RhodiumTheory.tex
more mods

Begin this section by showing a chart that tracks the effect of conflict duration on economic performance. The purpose of the chart would be to show that long running conflicts are not permanently depressing economic performance.

@@

>>>>

Begin this section by showing a chart that tracks the effect of conflict duration on economic performance in the aggregate. The purpose of the chart would be to show that long running conflicts are not permanently depressing economic performance.

thesis: conflicts only significantly dampens economic performance if they are a threat to major population centers. conflicts isolated in sparsely populated territories of the country have little to no effect on the whole.

@@

	maps: would be cool if maybe we could show the progression of a certain conflict across time and space. according to our theory what we would expect to happen as a conflict gets farther away from population centers is for econ performnace to improve. on the other hand, a conflict that moves closer and closer to population centers should lead to declined in econ performance.

End with a chart to show the distribution of econ performance among conflict-cntry-years to illustrate that there is noticeable variation in economic performance to explain. ending with this might help us lead into the empirics section and

	seems like the density plot you've already made in the models.R file highlights that the gdp growth var is kind of normal centered at zero which is good for us
